Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-07-22 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

\documentclass[apj]{emulateapj}

%Specify packages
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[tight]{subfigure}
\usepackage[breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}
\usepackage[utf8]{inputenc} %force unicode in bibtex
\usepackage{enumitem}
%use for editing/highlighting
\usepackage{color,soul}
%\usepackage{lineno}

@@

	\author{W. T. Barnes}
	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}
	\email{will.t.barnes@rice.edu}
	\author{P. J. Cargill}
	\affil{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW}
	\affil{School of Mathematics and Statistics, University of St Andrews, St Andrews, Scotland KY16 9SS}

@@

	\author{S. J. Bradshaw}
	\affil{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892}

@@

@@

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected. \hl{EXPAND/MODIFY??}

@@

	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \hl{(REFERENCES??)}. While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEU, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

		\includegraphics[width=\columnwidth]{figures/heating_functions.pdf}

@@

	\par We now show the results of our loop simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_single_a25.pdf}

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_ion_a25.pdf}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green). Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$. Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.

@@

	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures. $\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy-driven cooling. $\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons. As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating. As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures since radiative cooling is very inefficient at low densities and the heat flux saturates. In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle. The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. Contrastingly, on the hot side, the $\beta=0$ and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}. This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case. On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar. However, for $t_N\ge1500$ s, in the electron heating case, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK. This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK. In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.

@@

	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution. On the hot side, for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.

@@

	\par The dashed lines in the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the corresponding $\mathrm{EM}(T_{eff})$ for each heating function type. Only the mean $\mathrm{EM}(T_{eff})$ over $N_R$ runs is shown for these results. In all three figures, for the intermediate to high frequencies (i.e. $t_N\le1500$ s), there is no discernible difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$. Furthermore, both of the power-law cases show little deviation from ionization equilibrium in the emission measure for even the lowest heating frequencies in the single-fluid, electron heating, and ion heating cases. For $t_N\ge2500$ s in the uniform heating case, in both \autoref{fig:single_em} and \autoref{fig:el_em}, $\mathrm{EM}(T_{eff})$ is truncated at slightly lower temperatures as compared to $\mathrm{EM}(T)$. This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK. None of the panels of \autoref{fig:ion_em} show any significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$. This is because the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium during the entire heating phase.

@@

		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn2500_electron.pdf}

@@

	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.

@@

	\par\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions. In the uniform heating rate case (red), each event has a max heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively. Recall from \autoref{eq:heating_rate_constraint} that the total energy injected into the loop is constrained such that $H_0=(1/N)\sum_{i=1}^NH_i$. In the case where the heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$. 

@@

	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g. $t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical. In this way, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.
	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$. Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$. From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$. In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s. So even for the lowest heating frequency in the uniform case, the heating rate is still much lower. Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff. On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times). This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.

@@

		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}

@@

	\par We now examine several observables often used to characterize the emission measure distribution. The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2<a<5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively. We select a single sample run from our parameter space in which only the electrons are heated by the events chosen from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s. We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$. The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}
		}
		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}
		}

@@

		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}
		}
		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
		}

@@

	\clearpage

>>>>

\documentclass[preprint2,linenumbers]{aastex}

%Specify packages
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[all]{hypcap}
\usepackage[utf8]{inputenc} %force unicode in bibtex
\usepackage{enumitem}

@@

	\author{W. T. Barnes\altaffilmark{1}}
	\author{P. J. Cargill\altaffilmark{2,3}}

@@

	\author{S. J. Bradshaw\altaffilmark{1}}
	%affiliations
	\altaffiltext{1}{Department of Physics \& Astronomy, Rice University, Houston, TX 77251-1892; will.t.barnes@rice.edu, stephen.bradshaw@rice.edu}
	\altaffiltext{2}{Space and Atmospheric Physics, The Blackett Laboratory, Imperial College, London SW7 2BW; p.cargill@imperial.ac.uk}
	\altaffiltext{3}{School of Mathematics and Statistics, University of St Andrews, St Andrews, Scotland KY16 9SS}

@@

	%Keywords
	\keywords{Sun:corona, Sun:nanoflares, plasmas, hydrodynamics}

@@

	\par\authorcomment1{Maybe intro is a bit lengthy...where to cut it down?}

@@

	\par An analogous approach can be used to investigate the properties of the ``hot" coronal component expected from nanoflare heating, and is the subject of the present series of papers. In \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we looked at the hot plasma properties due to a single isolated nanoflare. The effects of heating pulse duration, changes to conductive cooling due to heat flux limiting, differential heating of electrons and ions, and non-equilibrium ionization (NEI) were studied. It was shown that signatures of nanoflare heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. The prospect of measurable signatures above $10$ MK was found to be diminished for short heating pulses (with duration $<100$ s), NEI, and differential heating of the ions rather than the electrons. It is important to stress for a single nanoflare that while the ``hot'' plasma is present, it cannot actually be detected.

@@

	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEU, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

		\plotone{figures/heating_functions.pdf}

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\plotone{figures/em_grid_single_a25.pdf}

@@

		\plotone{figures/em_grid_electron_a25.pdf}

@@

		\plotone{figures/em_grid_ion_a25.pdf}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green). Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$. Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) of each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures. The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop so that the loops cools to lower temperatures before being reheated. The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}. The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. As in \citetalias{barnes_inference_2016}, the results below $T_m$ are relatively independent of which species is heated.

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated. For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power law distribution leads to a broader distribution above $T_m$. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for the power laws with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}. This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power law distributions, in both the $\beta=1$ and $\beta=0$ cases.

@@

	\par From these initial results, there is an important difference in the information available in potential observations. Below $T_m$ the value of $a$ requires a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}. Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs. Taken together, the overall conclusion is the same: nanoflares require an \textit{intermediate frequency}. 

@@

	\par For electron heating, the $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em} evolve similarly to those shown in \autoref{fig:single_em}, especially on the cool side where the density is sufficiently high such that the electrons and the ions to equilibrate. On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar. However, for $t_N\ge1500$ s, in the electron heating case, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK. This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK. In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures. The conclusions regarding the role of NEI are similar to those in the single-fluid case: it is not a factor when the heating rates are determined by a power-law. In the uniform case, the hot emission is again truncated and relocated to cooler temperatures, with more pronounced ``bump'' in the $\mathrm{EM}(T)$ near $10$ MK.

@@

	\par When only the ions are heated (\autoref{fig:ion_em}), the cool side of the $\mathrm{EM}(T)$ is again very similar to both the single-fluid and electron heating cases due to equilibration. On the hot side, for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}. Regarding the role of NEI, there is no significant difference between $\mathrm{EM}(T)$ and $\mathrm{EM}(T_{eff})$ for either the uniform or power-law cases. Here the electrons are essentially heated on a timescale dictated by the Coulomb collision frequency which is slow enough to ensure ionization equilibrium throughout the heating and conductive cooling phases.

@@

		\plotone{figures/nT_sample_curves_tn2500_electron.pdf}

@@

	\par In \citet{cargill_active_2014}, \citetalias{barnes_inference_2016}, and \autoref{subsec:em_dist}, we have suggested that the plasma density prior to the nanoflare occuring is a crucial parameter in determining the emission measure distribution. This arises in two distinct ways. Below $T_m$, the temperature and density at which the nanoflare occurs cuts off the emission at lower temperatures. When combined with an energy-dependent waiting time, this can lead to a range of EM slopes in this region \citep{cargill_active_2014}. Above $T_m$, the initial density determines the temperature increase due to the nanoflare, how quickly the initial hot plasma cools, and whether NEI effects are important. We now examine this further.

@@

	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}. \autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions. In the uniform heating rate case (red), each event has a maximum heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively. 

@@

	\par In comparing various heating models, we insist that the total energy injected into the loop is the same for each run (see \autoref{eq:heating_rate_constraint}). When the nanoflare heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$. These few high energy events lead to $T\gg T_{max,0}$ (blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is sufficiently dense due to the draining and cooling times being longer than the time since the previous event, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). In the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g. $t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical. Thus, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.

@@

		\plotone{figures/em_slope_varying_bounds.pdf}
		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}

@@

	\par We now examine several observables often used to characterize the emission measure distribution. The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $a$ and $b$ can be calculated from the cool and hot sides of $\mathrm{EM}(T)$, respectively. We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s. We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K. The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

		\plottwo{figures/ratio_hist_alpha_electron_T2.pdf}{figures/ratio_hist_twait_electron_T2.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_ion_T2.pdf}{figures/ratio_hist_twait_ion_T2.pdf}

@@
